Algebraic File Synchronization: Adequacy and Completeness

### 2017-10-08 p2/ordering.tex
Symbol for sequences from sets; improvements

\begin{mydev}[$\orderd{S}$]
It follows from \cref{simple_reorder_equiv} that given a simple set of commands $S$,
which can be applied to a filesystem without breaking it,
all sequences in $\orderset{S}$
represent the same partial endofunction on filesystems.
This allows us to treat such a set as a sequence for any purpose
where the internal order of the commands is irrelevant.
We write $\orderd{S}$ to represent this endofunction.
\end{mydev}

>>>>

\begin{mydef}[$\ordsign$]
It follows from \cref{simple_reorder_equiv} that given a simple set of commands $S$,
which can be applied to a filesystem in some order without breaking it,
this order will be in $\orderset{S}$,
and all sequences in $\orderset{S}$
represent the same partial endofunction on filesystems.
This allows us to treat such a set as a sequence for any purpose
where the internal order of the commands is irrelevant.
We write $\ordp{S}$ to represent this endofunction.
Also, let $\ordp{S}=\cbrk$ if such an order does not exist.
\end{mydef}

### 2017-10-08 p2/rec-intro.tex
Symbol for sequences from sets; improvements

We work based on the assumption that to achieve this, we need
to apply to $\FS_B$ the commands that have been applied to $\FS_A$, and \emph{vice versa}.
As some commands may have been applied to both filesystems, our first approximation
is $\reca = A\setminus B$ and $\recb = B\setminus A$
(in some suitable order).
This, however, will break both filesystems if there have been incompatible updates
in $A$ and $B$. 
Our aim is therefore to provide an algorithm that selects the commands 
$\reca \subset A\setminus B$
and $\recb \subset B\setminus A$ 
so that $\reca\aFS_B\neq\fsbroken$ and $\recb\aFS_A\neq\fsbroken$,
and show that these are the longest sequences with this property, that is,
adding any command left out from $\reca$ or $\recb$ will break the filesystems.

@@

\begin{mydef}[Reconciliation]\label{def:reconciliation}
We determine $\reca$---which we apply to $\FS_B$ 
to reconcile it with $\FS_A$---to be
the largest subset of $A\setminus B$
that is independent of $B\setminus A$,
where $A$ and $B$ are simple sequences representing
the updates applied to replicas $\FS_A$ and $\FS_B$:
\[ \reca = \{\alpha \whr \alpha\in \ambnp  \ \wedge\   \alpha\indep \bmanp \}. \]
\end{mydef}

>>>>

We work based on the assumption that to achieve this, we need
to apply to $\FS_B$ the commands that have been applied to $\FS_A$, and \emph{vice versa}.
As some commands may have been applied to both filesystems, our first approximation
is $\reca = \amb$ and $\recb = \bma$.
This, however, will break both filesystems if there have been incompatible updates
in $A$ and $B$. 
Our aim is therefore to provide an algorithm that selects the commands 
$\reca \subset A\setminus B$
and $\recb \subset B\setminus A$ 
so that $\reca\aFS_B\neq\fsbroken$ and $\recb\aFS_A\neq\fsbroken$,
and show that these are the longest sequences with this property, that is,
adding any further command from $\reca$ or $\recb$ will break the filesystems.

@@

\begin{mydef}[Reconciliation]\label{def:reconciliation}
We determine $\reca$---which we apply to $\FS_B$ 
to reconcile it with $\FS_A$---to be
the largest subset of $A\setminus B$
that is independent of $B\setminus A$,
where $A$ and $B$ are simple sequences representing
the updates applied to replicas $\FS_A$ and $\FS_B$:
\[ \reca = \ords{\alpha \whr \alpha\in \ambnp  \ \wedge\   \alpha\indep \bmanp }. \]
\end{mydef}

### 2017-10-08 p2/rec-sound.tex
Symbol for sequences from sets; improvements

\begin{myth}\label{reconciliation_correct}
If $A, B$ are simple, then $\worksmbb{A,B}{B\cc \reca}$,
where, to restate \cref{def:reconciliation},
\[ \reca = \{\alpha \whr \alpha\in \ambnp  \ \wedge\   \alpha\indep \bmanp \}. \]
\end{myth}

@@

\begin{mylem}\label{can_move_intersection}
Let $A$ and $B$ be two simple sequences so that $\worksmnilb{A, B}$.
Then their intersection, in some suitable order, is also defined on any filesystem
either of them is defined on:
$\worksm{A}{\orderset{\acbnp}}$, and, by symmetry,
$\worksm{B}{\orderset{\acbnp}}$.
\end{mylem}

@@

Let us consider therefore the marked command preceded by an unmarked command in $A$,
and let the marked command be $\cxynv$, 
and the preceding unmarked command be $\czwmv$:
\begin{gather*}
A = \cdots\cc  \czwmv\cc  \cxynv\cc  \cdots
\end{gather*}
As $A$ is simple and $\worksmnilb{A}$, from 
\cref{ax_distantrel_breaks,ax_directchild_breaks,ax_directparent_breaks}
we know that these commands can only be on incomparable nodes or form a construction or destruction pair.
In the first case, swapping the commands results in a sequence equivalent to $A$,
and we show that the last two cases are impossible as they would lead to contradiction.

@@

We now know that there is an $A'\equiv A$ in which commands in $\acbnp$
are at the beginning, and therefore 
from \cref{worksextpostfix} we know that
$\worksm{A}{\acbnp}$ and by symmetry $\worksm{B}{\acbnp}$.
\end{proof}

@@

Our theorem is therefore proven if we prove the following lemma,
in which we rename $\ambnp$ to $S$ and $\bmanp$ to $T$:
\newcommand{\condSimple}{(c1)}
\newcommand{\condDisj}{(c2)}
\newcommand{\condApr}{(c3)}
\newcommand{\condWork}{(c4)}
\begin{mylem}\label{reconciliation_correct_part}
If
   \begin{itemize}
   \item[\condSimple] $S$ and $T$ are simple sequences,
   \item[\condDisj] $S\cap T=\emptyset$,
   \item[\condApr] $S^*$ is the largest subset of $S$ where $S^*\indep T$, and
   \item[\condWork] $\worksmxb{\sqs{C}}{S,T}$ for some set of sequences $\sqs{C}$,
   \end{itemize}
then
\[ \worksmxb{\sqs{C}}{S^*}. \]
\end{mylem}

>>>>

\begin{myth}\label{reconciliation_correct}
If $A$ and $B$ are simple, then $\worksmbb{A,B}{B\cc \reca}$,
where, to restate \cref{def:reconciliation},
\[ \reca = \ords{\alpha \whr \alpha\in \ambnp  \ \wedge\   \alpha\indep \bmanp }. \]
\end{myth}

@@

\begin{mylem}\label{can_move_intersection}
Let $A$ and $B$ be two simple sequences so that $\worksmnilb{A, B}$.
Then their intersection is also defined on any filesystem
either of them is defined on:
$\worksm{A}{\ordp{\acbnp}}$, and, by symmetry,
$\worksm{B}{\ordp{\acbnp}}$.
\end{mylem}

@@

Let us consider therefore the marked command preceded by an unmarked command in $A$,
and let the marked command be $\cxynv$, 
and the preceding unmarked command be $\czwmv$:
\begin{gather*}
A = \cdots\cc  \czwmv\cc  \cxynv\cc  \cdots
\end{gather*}
As $A$ is simple and $\wrks{A}$, from 
\cref{ax_distantrel_breaks,ax_directchild_breaks,ax_directparent_breaks}
we know that these commands can only be on incomparable nodes or form a construction or destruction pair.
In the first case, swapping the commands results in a sequence equivalent to $A$,
and we show that the last two cases are impossible as they would lead to contradiction.

@@

We now know that there is an $A'\equiv A$ in which commands in $\acbnp$
are at the beginning, and therefore 
from \cref{worksextpostfix} we know that
$\worksm{A}{\acb}$ and by symmetry $\worksm{B}{\acb}$.
\end{proof}

@@

Our theorem is therefore proven if we prove the following lemma,
in which we rename $\amb$ to $S$ and $\bma$ to $T$:
\newcommand{\condSimple}{(c1)}
\newcommand{\condDisj}{(c2)}
\newcommand{\condApr}{(c3)}
\newcommand{\condWork}{(c4)}
\begin{mylem}\label{reconciliation_correct_part}
If
   \begin{itemize}
   \item[\condSimple] $S$ and $T$ are simple sequences,
   \item[\condDisj] $S\cap T=\emptyset$,
   \item[\condApr] $S^*$ is the largest subset of $S$ where $S^*\indep T$, and
   \item[\condWork] $\worksmxb{\sqs{C}}{S,T}$ for some set of sequences $\sqs{C}$,
   \end{itemize}
then
\[ \worksmxb{\sqs{C}}{S^*}. \]
\end{mylem}

### 2017-10-08 p2/works-inverse.tex
Symbol for sequences from sets; improvements

% TODO \alpha \neq \cbrk
\begin{mylem}\label{repr_comm_inject}
Representative commands $\alpha\T$ are partial bijections over representative filesystems
($\FS\T$, $\GS\T$).
Because partial functions are trivially surjective when restricted to their images, this is
equivalent to saying that representative functions are injective except for cases
where they are not defined:
\[ \forall\FS,\GS,\alpha: \FS\T\neq\GS\T \wedge \alpha\T(\FS\T)\neq\fsbroken \Longrightarrow \alpha\T(\FS\T) \neq \alpha\T(\GS\T). \]
\end{mylem}
\begin{proof}
Choose values that satisfy the left side, and let $\alpha\T = \cTxynv$.
If $\FS\T$ and $\GS\T$ have different values (types) at any node apart from $n$, then this difference remains
even after applying $\cTxynv$ to $\FS\T$. 
The only remaining case therefore is where they have the same values
at all nodes except at $n$.
As $\cTxynv(\FS\T)\neq\fsbroken$, we know $[\FS(n)]=[x]$.
We also know that $\GS\T(n)\neq\FS\T(n)$, and therefore
$[\GS(n)]\neq[x]$.
This implies $\cTxynv(\GS\T)=\fsbroken$,
and again we have $\alpha\T(\FS\T) \neq \alpha\T(\GS\T)$.
\end{proof}

@@

\begin{mylem}\label{r_invmove}
A common initial segment of a set of \emph{representative} sequences can be moved 
to the other side of $\worksmeqsign$ by inverting it:
\begin{gather*}
\worksm{\ia}{B\cc\ic}
\ \Longleftrightarrow \ \worksm{\ibi\cc\ia}{\ic} 
\ \wedge \  \worksm{\ia}{\{B\}}
\end{gather*}
\end{mylem}
\begin{proof}
% This result is quite expected as we're mapping a subset statement using a bijection,
% but made more complicated a as B is not defined everywhere.

>>>>

% TODO \alpha \neq \cbrk
\begin{mylem}\label{repr_comm_inject}
Representative commands $\alpha\T$ are partial bijections over representative filesystems
($\FS\T$, $\GS\T$).
Because partial functions are trivially surjective when restricted to their images, this is
equivalent to saying that representative functions are injective except for cases
where they are not defined:
\begin{align*}
\forall\FS,\GS,\alpha:& \\
& \FS\T\neq\GS\T \wedge \alpha\T(\FS\T)\neq\fsbroken \\
& \Rightarrow \alpha\T(\FS\T) \neq \alpha\T(\GS\T).
\end{align*}
\end{mylem}
\begin{proof}
Choose values that satisfy the left side, and let $\alpha\T = \cTxynv$.
If $\FS\T$ and $\GS\T$ have different values (types) at any node apart from $n$, then this difference remains
even after applying $\cTxynv$ to $\FS\T$. 
The only remaining case therefore is where they have the same values
at all nodes except at $n$.
As $\cTxynv(\FS\T)\neq\fsbroken$, we know $[\FS(n)]=[x]$.
We also know that $\GS\T(n)\neq\FS\T(n)$, and therefore
$[\GS(n)]\neq[x]$.
This implies $\cTxynv(\GS\T)=\fsbroken$,
and again we have $\alpha\T(\FS\T) \neq \alpha\T(\GS\T)$.
\end{proof}

@@

\begin{mylem}\label{r_invmove}
A common initial segment of a set of representative sequences can be moved 
to the other side of $\worksmeqsign$ by inverting it:
\begin{gather*}
\worksm{\ia}{B\cc\ic}
\ \Longleftrightarrow \ \worksm{\ibi\cc\ia}{\ic} 
\ \wedge \  \worksm{\ia}{\{B\}}
\end{gather*}
\end{mylem}
\begin{proof}
% This result is quite expected as we're mapping a subset statement using a bijection,
% but made more complicated a as B is not defined everywhere.
